Large-scale feature selection with Gaussian mixture models for the classification of high dimensional remote sensing images

### 2017-01-16 paper.tex
del -

The     remaining    of     the     article     is    organized     as
follows.   Section~\ref{sec:gmm-hd}  presents   GMM  classifiers   and
problems  related to  high-dimensional  feature  spaces. The  feature
selection methods are detailed in Section~\ref{sec:selection}. Then, an
efficient         implementation        is         presented        in
Section~\ref{sec:implementation}.  Experimental  results on  two  real
high dimensional data-sets are given Section~\ref{sec:test}. Conclusion
and perspectives conclude the paper in Section~\ref{sec:conclusion}.

@@

\section{Data-sets}
\label{sec:datasets}
Numerical experiments have been  conducted on two different data-sets.
The  first  one,  called  \emph{Aisa}, is  an  airborne  hyperspectral
dataset  and  the  second,  called \emph{Potsdam},  is  an  very  high
resolution multispectral airborne image.

>>>>

The     remaining    of     the     article     is    organized     as
follows.   Section~\ref{sec:gmm-hd}  presents   GMM  classifiers   and
problems  related to  high-dimensional  feature  spaces. The  feature
selection methods are detailed in Section~\ref{sec:selection}. Then, an
efficient         implementation        is         presented        in
Section~\ref{sec:implementation}.  Experimental  results on  two  real
high dimensional datasets are given Section~\ref{sec:test}. Conclusion
and perspectives conclude the paper in Section~\ref{sec:conclusion}.

@@

\section{Datasets}
\label{sec:datasets}
Numerical experiments have been  conducted on two different datasets.
The  first  one,  called  \emph{Aisa}, is  an  airborne  hyperspectral
dataset  and  the  second,  called \emph{Potsdam},  is  an  very  high
resolution multispectral airborne image.
